<!-- ===================================================================== -->
<!-- This file is generated from `r gsub(".*\\.tpl/",".tpl/",knitr::current_input(dir=TRUE))` -->
<!-- ===================================================================== -->


``` {r echo=FALSE, message=FALSE,INCLUDE=TRUE}

source("../lib/R/file.R")
source("../lib/R/image.R")


suppressPackageStartupMessages({
  library(here)
  library(RSQLite)
  library(forcats)
  library(tidyverse) 
  library(kableExtra)
})

scriptdir <- here()
```


# world-datas-analysis
miscellaneous worlds data and analysis

## Providers of dataset

``` {r echo=FALSE, message=FALSE,INCLUDE=TRUE}

provider <- read_fwf("../dataset/provider.txt")

provider %>%
  arrange(provider) %>%
  mutate(
    linkprovider = paste0("[",provider,"](dataset/",provider,")"),
    linkdescription = paste0("[",description,"](",website,")"),
    linknbdatasets = paste0("[",nb_datasets,"](dataset/",provider,"#",tolower(provider),"-datasets)"),
    linknbvariables = paste0("[",max_variables,"](dataset/",provider,"#",tolower(provider),"-variables)")
  ) %>%
  select (
    "Dataset" = linkprovider,
    "Description" = linkdescription,
    "Avg scope" = max_scope,
    "Nb datasets" = linknbdatasets,
    "Max variables" = linknbvariables,
    "Nb observations" = nb_observations
  ) %>%
  kable(format="pipe", escape = FALSE)
```

## Todo

| Status | Category                    | Scope       | Description                                                                                                                             | Sample Report                                                                                                       |
|--------|-----------------------------|-------------|-----------------------------------------------------------------------------------------------------------------------------------------|---------------------------------------------------------------------------------------------------------------------|
| [_]    | Geonames                    | Cities      | [Geonames](https://download.geonames.org/export/dump/)                                                                  | [International Covid-19](international/covid-19/README.md) / [French Covid-19](countries/french/covid-19/README.md) |
| [_]    | Covid                       | Countries   | [Johns Hopkins University](https://github.com/CSSEGISandData/COVID-19)                                                                  | [International Covid-19](international/covid-19/README.md) / [French Covid-19](countries/french/covid-19/README.md) |
| [_]    | Population                  | Countries   | [United nation](https://population.un.org/wpp/Download/Standard/Population/)                                                            |                                                                                                                     |
| [_]    | Population                  | Cities      | [insee](https://www.insee.fr/fr/information/2008354)                                                                                    |                                                                                                                     |
| [_]    | Population                  | Cities      | [insee estimation](https://www.insee.fr/fr/statistiques/1893198)                                                                        |                                                                                                                     |
| [_]    | Weather                     | Cities      | [European Climate Assessment & Dataset](https://www.ecad.eu/dailydata/predefinedseries.php)                                             |                                                                                                                     |
| [_]    | Weather                     | Cities      | [European Centre for Medium-Range Weather Forecasts](https://confluence.ecmwf.int/display/WEBAPI/Accessing+ECMWF+data+servers+in+batch) |                                                                                                                     |
| [_]    | bike counter                | Montpellier | [Montpellier 3M/Velocité](https://compteurs.velocite-montpellier.fr/)                                                                   |                                                                                                                     |
| [_]    | Rental bike                 | Montpellier | [Montpellier 3M](https://data.montpellier3m.fr/dataset/courses-des-velos-velomagg-de-montpellier-mediterranee-metropole)                |                                                                                                                     |
| [_]    | universitetetioslo          | Countries   | [CO2 emissions](https://folk.universitetetioslo.no/roberan/GCB2020.shtml)                                                               |                                                                                                                     |
| [_]    | NASA                        | Countries   | [Anormal température](https://data.giss.nasa.gov/gistemp/)                                                                              |                                                                                                                     |

## Init environment

```
# Python
python -m venv .venv
source .venv/bin/activate
pip install --only-binary=:all: -r requirements.txt

# R
renv::restore()
```

## Import and export datas

```
# All in one
./importer/<dataset>/import_and_export.sh
# or step by step
./importer/<dataset>/download.sh
./importer/<dataset>/import.sh
./importer/<dataset>/export.sh
```
## Update this Readme.md page
```
./build_rmarkdown_pages.sh
```


```
# Use virtualenn python environment
source .venv/bin/activate

# owid
importer/owid/download.sh
importer/owid/import.sh


# Level 1 (geoname)
importer/geonames/download.sh
importer/geonames/import.sh

# Worldbnk
python importer/200-worldbank/download.py
sqlite3 -bail world-datas-analysis.db < importer/200-worldbank/import.sql
#international/countryexport_worldbank.sh
#python international/country/download_from_ourworldindata.py

# Vigilo
./importer/vigilo/import_and_export.sh

# Summary
sqlite3 -bail world-datas-analysis.db < db_summary.sql
```